---
title: "ST501 Group Project"
author: "Michael DeWitt"
date: "7/20/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Introduction

# Part 1 Convergences

## A

## B

## C
Derrive the CDF of the double exponential distribution.

$$f_Y(y) = \frac{1}{2b} * e^{-(\frac{|{y-\mu|)}}{b})}$$

This yields two cases for the CDF:

$$
F_Y(y)=
\begin{cases}
\int_{-\infty}^tf_Y(Y)dt & \text{for } y \le \mu \\
\int^{\infty}_tf_Y(Y)dt & \text{for } y \ge \mu \\
\end{cases}
$$

Solving for these leaves us with the following:

For $y \le \mu$ :

$$\int_{-\infty}^tf_Y(Y)dt$$
$$\int_{-\infty}^t\frac{1}{2b} * e^{-(\frac{{t-\mu}}{b})}dt$$
We know that in this case we are solving for when the exponent is positive.

$$\int_{-\infty}^t\frac{1}{2b} * e^{(\frac{|{t-\mu|)}}{b})}dt$$

$$\frac{1}{2b} * e^{(\frac{t-\mu}{b})}*b|_{-\infty}^{t}=\frac{1}{2}e^{(\frac{t-\mu}{b})} - 0 = \frac{1}{2}e^{(\frac{t-\mu}{b})}$$

For the case where $y \ge \mu$

$$\int_{-\infty}^tf_Y(Y)dt$$

$$\int_{-\infty}^t\frac{1}{2b} * e^{-(\frac{{t-\mu}}{b})}dt$$

This must be further split into:

$$\int_{-\infty}^\mu\frac{1}{2b} * e^{-(\frac{{t-\mu}}{b})}dt + \int_{\mu}^t\frac{1}{2b} * e^{-(\frac{{t-\mu}}{b})}dt$$

$$\frac{1}{2b} * e^{(\frac{-t+\mu}{b})}*-b|_{-\infty}^{\mu} + \frac{1}{2b} * e^{(\frac{-t+\mu}{b})}*-b|_{\mu}^{t}$$

$$\frac{1}{2} - e^{\frac{\mu-t}{b}} + \frac{1}{2}$$

Thus for this case:

$$1-e^{\frac{\mu-t}{b}}$$

In conclusion the CDF for the double exponential distribution is:

$$
F_Y(y)=
\begin{cases}
\frac{1}{2}e^{(\frac{t-\mu}{b})} & \text{for } y \le \mu \\
1-e^{\frac{\mu-t}{b}} & \text{for } y \ge \mu
\end{cases}
$$

## D


```{r}

model_grid <- tibble(N = 50,
                     n = seq(1, 250, 1))


rdoublex <- function(mu, b, u){
  b*log(2*u) + mu
}

my_list <-list()
for(i in 1:250){
  random_uniform <- runif(i)
  out <- mean(rdoublex(mu = 0,b = 5,u = random_uniform))
  
  my_list[[i]] <- data.frame(n = i, mu = out)
}



```

## E